---
title: "MassExpression"
output:
  github_document:
    toc: yes
---

Universal Imports + High Quality QC + Differential Expression Analysis = Awesomeness. 

# Workflow example

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      collapse = TRUE,
                      comment = "#>", 
                      fig.width = 6, fig.height = 6)
```


## Setup 

```{r eval=FALSE}
library(devtools)
library(tibble)
devtools::install_github("MassExpression")
```


```{r eval=TRUE}
library(plotly)
library(stringr)

library(MassExpression)
utils::packageVersion("MassExpression")
```

## Internal data available 

```{r}
data(package="MassExpression")
```


## Run workflow with sample data


```{r eval=FALSE}
intensities <- mq_lfq_data$intensities
design <- mq_lfq_data$design
parameters <- mq_lfq_data$parameters
normalisation_method <- parameters[parameters[,1] == "UseNormalisationMethod",2]
species <- parameters[parameters[,1] == "Species",2]
labellingMethod <- parameters[parameters[,1] == "LabellingMethod",2]


results <- runGenericDiscovery(experimentDesign = design, 
                               proteinIntensities = intensities, 
                               normalisationMethod = normalisation_method, 
                               species = species, 
                               labellingMethod = labellingMethod)

IntensityExperiment <- results$IntensityExperiment
CompleteIntensityExperiment <-  results$CompleteIntensityExperiment
design <- colData(CompleteIntensityExperiment)
```


`results` is a list containing two `SummarizedExperiment` objects:

  - `IntensityExperiment`: contains the raw data (including missing values)
  
  - `CompleteIntensityExperiment`: contains the imputed data and summary statistics about the number of replicates and imputed proteins in each group of the conditions of interest. 


# Generate vignette

```{r eval=FALSE}
tools::buildVignettes(dir = ".", tangle=TRUE)
```


# Save output and create QC reports

```{r fragpipe, eval=FALSE}
output_folder <- "path/to/output/folder"

saveOutput(IntensityExperiment = IntensityExperiment, 
CompleteIntensityExperiment = CompleteExperiment, output_folder =  output_folder)
```

## Render QC 

```{r render-qc, eval=FALSE}
# Render and save QC report 
qc_report <- system.file("rmd","QC_report.Rmd", package = "MassExpression")

rmarkdown::render(qc_report,
                  params = list(listInt = listIntensityExperiments,
                                experiment = "Mass Dynamics QC report",
                                output_figure = file.path(output_folder, "figure_html/"),
                                format = "html"),
                  output_file = file.path(output_folder, "QC_Report.html"),
                  output_format=rmarkdown::html_document(
                            self_contained=FALSE,
                            lib_dir=file.path(output_folder,"qc_report_files"),
                            code_folding= "hide",
                            theme="united",
                            toc = TRUE,
                            toc_float = TRUE,
                            fig_caption= TRUE,
                            df_print="paged"))
# Render PDF
rmarkdown::render(qc_report,
                  params = list(listInt = listIntensityExperiments,
                                experiment = "Mass Dynamics QC report",
                                output_figure = file.path(output_folder_pdf, "figure_pdf/"),
                                format = "pdf"),
                  output_file = file.path(output_folder_pdf, "QC_Report.pdf"),
                  output_format=rmarkdown::pdf_document(
                    toc = TRUE,
                    fig_caption= TRUE))
```



# Session Information

```{r}
sessionInfo()
```
