---
title: "Introduction to MassExpression"
author: "Mass Dynamics"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: yes
    toc_float: true
  rmarkdown::html_vignette:
    fig_caption: yes
    toc_float: true
vignette: >
  %\VignetteIndexEntry{Introduction to MassExpression}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
library(plotly)
library(stringr)
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      collapse = TRUE,
                      comment = "#>")
```


# Setup 

```{r eval=FALSE}
library(devtools)
devtools::install_github("XXX")
```


```{r eval=TRUE}
library(MassExpression)
utils::packageVersion("MassExpression")
```

```{r}
ls("package:MassExpression")
```

# Internal data available 

```{r}
data(package="MassExpression")
```


# Run workflow with sample data


```{r}
intensities <- mq_lfq_data$intensities
design <- mq_lfq_data$design
parameters <- mq_lfq_data$parameters
normalisation_method <- parameters[parameters[,1] == "UseNormalisationMethod",2]
species <- parameters[parameters[,1] == "Species",2]
labellingMethod <- parameters[parameters[,1] == "LabellingMethod",2]


results <- runGenericDiscovery(experimentDesign = design, 
                               proteinIntensities = intensities, 
                               normalisationMethod = normalisation_method, 
                               species = species, 
                               labellingMethod = labellingMethod)

IntensityExperiment <- results$IntensityExperiment
CompleteIntensityExperiment <-  results$CompleteIntensityExperiment
```


# Plot results

## PCA

```{r pca-imputed, fig.width = 8, fig.height = 6}
## PCA
p=pca_plot_experiment(CompleteIntensityExperiment, format = "html")
p[[1]]
```

```{r  scree-plot-pca, fig.width = 6, fig.height = 4}
p[[2]]
```



## MDS

```{r mds-impute, fig.width = 6, fig.height = 4}
# 
p=mds_plot_experiment(CompleteIntensityExperiment)
p[[1]]
```

```{r fig.width = 6, fig.height = 4}
p[[2]]
```

## B. Quantitative values CV distributions {.tabset .tabset-fade .tabset-pills}

```{r cv-dist, fig.width = 8, fig.height = 5}
plot_condition_cv_distribution(IntensityExperiment)
```


## C. Intensity distribution across runs {.tabset .tabset-fade .tabset-pills}


```{r rle-plots, fig.width = 8, fig.height = 6}
normalised <- FALSE
if(metadata(CompleteIntensityExperiment)$NormalisationAppliedToAssay != "None"){
  normalised <- TRUE
}

# Plot RLE of log2 raw intensity as well as RLE of normalised 
p_raw <- plot_rle_boxplot(IntensityExperiment, CompleteIntensityExperiment, 
                    includeImputed = FALSE, plotRawRLE = TRUE)
p_raw <- p_raw + ggtitle("RLE of log2 Processed Intensities") 
fig <- makeRLEBoxplotInteractive(p_raw)
fig
```
  
  
```{r fig.width = 8, fig.height = 6}
if(normalised){
  # Plot RLE of log2 raw intensity as well as RLE of normalised 
  p_norm <- plot_rle_boxplot(IntensityExperiment, CompleteIntensityExperiment, 
                      includeImputed = FALSE, plotRawRLE = FALSE)
  p_norm <- p_norm + ggtitle("RLE of Normalised Intensities") 
  fig <- makeRLEBoxplotInteractive(p_norm)
}
fig
```
  
  
# 3. Feature completedness {.tabset .tabset-fade .tabset-pills}

## By sample

```{r sample-missingness, fig.width = 8, fig.height = 6}
p <- replicate_missingness_experiment(IntensityExperiment)
ggplotly(p, tooltip = c("y")) %>% config(displayModeBar = T, 
                                                  modeBarButtons = list(list('toImage')),
                                                  displaylogo = F)
```


## By protein

```{r protein-missingness, fig.width = 6, fig.height = 6}
p <- protein_missingness_experiment(IntensityExperiment)
ggplotly(p, tooltip = c("y")) %>% config(displayModeBar = T, 
                                                  modeBarButtons = list(list('toImage')),
                                                  displaylogo = F)
```


## Clustering of samples and proteins using missing values

```{r fig.width = 8, fig.height = 6}
plot_heatmap_missingness(IntensityExperiment)
```


# 4. Imputed versus non imputed log2 intensity values


```{r compare-imputed , fig.width = 6, fig.height = 6}
plot_imputed_vs_not(CompleteIntensityExperiment = CompleteIntensityExperiment)
```


# 5. Model QC

## Volcano plots

```{r fig.width = 6, fig.height = 6}
stats <- rowData(CompleteIntensityExperiment)
logfcs <- colnames(stats)[stringr::str_detect(colnames(stats), "logFC.")]
for(lfc in logfcs){
  comp_name <- stringr::str_remove(lfc, "logFC.")
  adj <- paste0("adj.P.Val.",comp_name)
  adjp <- colnames(stats)[stringr::str_detect(colnames(stats), adj)]
  pval <- paste0("P.Value.",comp_name)
  pval_col <- colnames(stats)[str_detect(colnames(stats), pval)]
  comparison.statistics <- data.frame(FoldChange=stats[,lfc],
                                      AdjustedPValue=stats[,adjp], 
                                      PValue = stats[,pval_col],
                                      ProteinId=stats$ProteinId, comparison=comp_name)
  print(plot_volcano(comparison.statistics))
  
}
```


## MA plot

```{r fig.width = 6, fig.height = 6}
for(lfc in logfcs){
  comp_name <- str_remove(lfc, "logFC.")
  comparison.statistics <- data.frame(FoldChange=stats[,lfc],
                                      AveExpr=stats$AveExpr, 
                                      ProteinId=stats$ProteinId, comparison=comp_name)
  print(plot_ma(comparison.statistics))
  
}
```



## Histogram of pvalues

```{r fig.width = 6, fig.height = 6}
pvals <- colnames(stats)[str_detect(colnames(stats), "P.Value.")]
for(pval in pvals){
  comp_name <- str_remove(pval, "P.Value.")
  print(hist(stats[,pval], main=comp_name))
  
}
```


# 6. Session Information

```{r}
sessionInfo()
```

