---
title: "Introduction to MassExpression"
author: "Mass Dynamics"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_caption: yes
    toc_float: true
vignette: >
  %\VignetteIndexEntry{Introduction to MassExpression}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
library(plotly)
library(stringr)
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      collapse = TRUE,
                      comment = "#>", 
                      fig.width = 6, fig.height = 6)
```


# Setup 

```{r eval=FALSE}
library(devtools)
library(tibble)
devtools::install_github("MassExpression")
```


```{r eval=TRUE}
library(MassExpression)
utils::packageVersion("MassExpression")
```

# Internal data available 

```{r}
data(package="MassExpression")
```


# Run workflow with sample data


```{r}
intensities <- mq_lfq_data$intensities
design <- mq_lfq_data$design
parameters <- mq_lfq_data$parameters
normalisation_method <- parameters[parameters[,1] == "UseNormalisationMethod",2]
species <- parameters[parameters[,1] == "Species",2]
labellingMethod <- parameters[parameters[,1] == "LabellingMethod",2]


results <- runGenericDiscovery(experimentDesign = design, 
                               proteinIntensities = intensities, 
                               normalisationMethod = normalisation_method, 
                               species = species, 
                               labellingMethod = labellingMethod)

IntensityExperiment <- results$IntensityExperiment
CompleteIntensityExperiment <-  results$CompleteIntensityExperiment
design <- colData(CompleteIntensityExperiment)
```


# Plot results

# 1. Experiment Design and Summary of Results


- **Species** of experiment: `r metadata(CompleteIntensityExperiment)$Species`

- **Normalisation method applied to assay**: `r metadata(CompleteIntensityExperiment)$NormalisationAppliedToAssay`


```{r experimental-design, eval=TRUE, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE, results='asis'}
design <- tibble::as_tibble(design)
design$SampleName <- make.names(design$SampleName)
design <- design %>% tidyr::unite(SampleNameInPlots, Condition, Replicate, 
                                                      sep="_", remove=FALSE) %>%
  dplyr::select(-Replicate, everything())

design <- design %>% dplyr::select(SampleName, Condition, 
                SampleNameInPlots, everything())
  

knitr::kable(design, row.names = FALSE) 
```

\clearpage

The table below reports the number of proteins (*Number of Proteins* column) considered for each pairwise comparison analysis (proteins with more than 50% missing values across samples are removed) and the number of DE proteins detected in each comparison (*Number DE Proteins* column). The overall total number of proteins included in the exeriment is `r nrow(rowData(CompleteIntensityExperiment))`.


```{r  summary-de, eval=TRUE, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE, results='asis'}
stats <- tibble::as_tibble(rowData(CompleteIntensityExperiment))
pval_proteins <- stats %>%
  dplyr::select(ProteinId, starts_with("adj.P.Val"))

total_proteins_in_experiment <- nrow(pval_proteins)
total_proteins_de <- length(pval_proteins$adj.P.Val < 0.05)

n_proteins_by_cond <- pval_proteins
n_proteins_by_cond$adj.P.Val <- NULL

n_proteins_by_cond_long <- n_proteins_by_cond %>% tidyr::pivot_longer(cols = starts_with("adj.P.Val"), names_to = "Comparison",values_to = "AdjPval")
n_proteins_by_cond_long$Comparison <- gsub("adj.P.Val.", "", n_proteins_by_cond_long$Comparison)

summary_de <- n_proteins_by_cond_long %>% 
  group_by(Comparison) %>%
  summarise(`Number of Proteins` = sum(!is.na(AdjPval)),
            `Number DE Proteins` = sum(AdjPval < 0.05, na.rm = TRUE))

knitr::kable(summary_de, row.names = FALSE, caption="Summary of differential expression results across comparisons.") 
```

# 2. Experiment Health

## A. Dimensionality reduction {.tabset .tabset-fade .tabset-pills}

```{r pca-imputed}
## PCA
p=plot_chosen_pca_experiment(CompleteIntensityExperiment, assayName = "intensities", format = "html")
p[[1]]
```

```{r  scree-plot-pca}
p[[2]]
```

```{r pca-imputed-de}
p=plot_chosen_pca_experiment(CompleteIntensityExperiment, assayName = "intensities", format = "html", auto_select_features = "de")
p[[1]]
```

## B. Quantitative values CV distributions {.tabset .tabset-fade .tabset-pills}

```{r cv-dist}
p=plot_condition_cv_distribution(IntensityExperiment)
ggplotly(p[[1]]) %>% plotly::config(displayModeBar = T, 
                        modeBarButtons = list(list('toImage')),
                        displaylogo = F)
```

  
```{r cv-table, eval=TRUE, warning=FALSE, echo=FALSE, error=FALSE, message=FALSE, results='asis'}
cv_data <- p[[2]]
cv_data <- tibble::as_tibble(cv_data) %>% group_by(Condition) %>%
  summarise(`Median CV %` = round(median(cv, na.rm = TRUE)*100))

knitr::kable(cv_data, row.names = FALSE)
```

  
## C. Sample correlations


```{r corr-samples}
plot_samples_correlation_matrix(CompleteIntensityExperiment, assayName = "intensities")
```


```{r corr-samples-de}
plot_samples_correlation_matrix(CompleteIntensityExperiment,assayName = "intensities", onlyDEProteins = TRUE)
```
  
# 3. Feature completedness {.tabset .tabset-fade .tabset-pills}

## Patterns of missing values

```{r missing-pattern}
plot_missingness_heatmap(IntensityExperiment)
```


## By sample

```{r sample-missingness}
p <- plot_replicate_missingness(IntensityExperiment, assayName = "raw")
ggplotly(p, tooltip = c("y")) %>% plotly::config(displayModeBar = T, 
                                                  modeBarButtons = list(list('toImage')),
                                                  displaylogo = F)
```


## By protein

```{r protein-missingness}
p <- plot_protein_missingness(IntensityExperiment, assayName="raw")

ggplotly(p, tooltip = c("y")) %>% plotly::config(displayModeBar = T, 
                                                  modeBarButtons = list(list('toImage')),
                                                  displaylogo = F)
```


# 4. Identifications {.tabset .tabset-fade .tabset-pills}

## Counts

```{r identifications-by-sample}
plot_n_identified_proteins_by_replicate(IntensityExperiment)
```

## Consistent across conditions 

```{r consistent-identifications-across-repl}
plot_consistent_proteins_by_replicate(IntensityExperiment)
```

# 5. Normalisation and Imputation


## A. Intensities distribution (before and after normalisation) {.tabset .tabset-fade .tabset-pills}

### Raw intensities


```{r raw-boxplots}
normalised <- FALSE
if(metadata(CompleteIntensityExperiment)$NormalisationAppliedToAssay != "None"){
  normalised <- TRUE
}

# Plot RLE of log2 raw intensity as well as RLE of normalised 
p_raw <- plot_log_measurement_boxplot(IntensityExperiment, title = "log2 Raw Intensities", format = "html")
p_raw 
```

### RLE (median centered protein intensities)


```{r rle-plots}
normalised <- FALSE
if(metadata(CompleteIntensityExperiment)$NormalisationAppliedToAssay != "None"){
  normalised <- TRUE
}

# Plot RLE of log2 raw intensity as well as RLE of normalised 
p_raw <- plot_rle_boxplot(IntensityExperiment, CompleteIntensityExperiment, 
                    includeImputed = FALSE, plotRawRLE = TRUE, 
                    title = "RLE of log2 Raw Intensities", 
                    format = "html")
p_raw 
```
  
  
```{r}
if(normalised){
  # Plot RLE of log2 raw intensity as well as RLE of normalised 
  p_norm <- plot_rle_boxplot(IntensityExperiment, CompleteIntensityExperiment, 
                      includeImputed = FALSE, plotRawRLE = FALSE)
  p_norm <- p_norm + ggtitle("RLE of Normalised log2 Intensities") 
  
  p_norm
}
```
  

## B. Imputed vs actual intensities {.tabset .tabset-fade .tabset-pills}


```{r compare-imputed}
plot_imputed_vs_not(CompleteIntensityExperiment = CompleteIntensityExperiment)
```


# 5. Model QC

## Volcano plots

```{r fig.width = 6, fig.height = 6}
stats <- rowData(CompleteIntensityExperiment)
logfcs <- colnames(stats)[stringr::str_detect(colnames(stats), "logFC.")]
for(lfc in logfcs){
  comp_name <- stringr::str_remove(lfc, "logFC.")
  adj <- paste0("adj.P.Val.",comp_name)
  adjp <- colnames(stats)[stringr::str_detect(colnames(stats), adj)]
  pval <- paste0("P.Value.",comp_name)
  pval_col <- colnames(stats)[str_detect(colnames(stats), pval)]
  comparison.statistics <- data.frame(FoldChange=stats[,lfc],
                                      AdjustedPValue=stats[,adjp], 
                                      PValue = stats[,pval_col],
                                      ProteinId=stats$ProteinId, comparison=comp_name)
  print(plot_volcano(comparison.statistics))
  
}
```


## MA plot

```{r fig.width = 6, fig.height = 6}
for(lfc in logfcs){
  comp_name <- str_remove(lfc, "logFC.")
  comparison.statistics <- data.frame(FoldChange=stats[,lfc],
                                      AveExpr=stats$AveExpr, 
                                      ProteinId=stats$ProteinId, comparison=comp_name)
  print(plot_ma(comparison.statistics))
  
}
```



## Histogram of pvalues

```{r fig.width = 6, fig.height = 6}
pvals <- colnames(stats)[str_detect(colnames(stats), "P.Value.")]
for(pval in pvals){
  comp_name <- str_remove(pval, "P.Value.")
  print(hist(stats[,pval], main=comp_name))
  
}
```


# 6. Session Information

```{r}
sessionInfo()
```

