---
title: "Feature completedness by protein"
output:
  html_document:
    theme: united
    toc: no
    fig_caption: yes
    lib_dir: qc_report_files
params:
  listInt: empty
  experiment: empty
  format: pdf
  output_figure: figures
---


<style type="text/css">

summary {
  text-decoration: underline;
  font-size: 16px;
  color: grey;
  cursor: pointer;
  margin-bottom: 16px;
}

summary, summary:active {
  border: none;
}

details span {
  margin-top: 8px;
  display: block;
}

#header .btn-group {
  display: none;
}

.main-container {
  max-width: 1400px !important;
}
</style>

--- 

```{r setup, include=FALSE}
print(params)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
                      fig.path = params$output_figure, dev = "svg")
```


```{r data-needed, include=FALSE, eval=TRUE}
library(dplyr)
library(stringr)
library(MassExpression)
library(plotly)

CompleteIntensityExperiment <- params$listInt$CompleteIntensityExperiment
IntensityExperiment <- params$listInt$IntensityExperiment
design <- colData(IntensityExperiment)

comparisonExperiments <- 
    listComparisonExperiments(CompleteIntensityExperiment)
```


<details>
  <summary>Distribution of missing values by samples and by proteins</summary>
  <span>
    <p> The amount of missing values can be affected by the biological condition or by technical factors and it can vary largely between experiments.</p>
   <p>For a healthy experiment we expect:</p>
    <ul>
      <li>The distribution of missing values by replicate to be similar across replicates, especially within the same biological conditions</li>
    </ul>
    <p>There isns't a strict threshold to look for in terms of % of missing values. However, an unusually large amount of missingness in one or a few replicates can be sympthomatic of technial problems and should be taken into account when intepreting the final differential expression results.<p>
  </span>
</details> 


```{r protein-missingness}
p <- plot_protein_missingness(IntensityExperiment)
if (params$format == "pdf"){
  p
} else {
  ggplotly(p, tooltip = c("y")) %>% plotly::config(displayModeBar = T, 
                                                  modeBarButtons = list(list('toImage')),
                                                  displaylogo = F)
}
```


