---
title: "RLE of Log2 raw intensities"
output:
  html_document:
    theme: united
    toc: no
    fig_caption: yes
    lib_dir: qc_report_files
params:
  listInt: empty
  experiment: empty
  format: pdf
  output_figure: figures
---


<style type="text/css">

summary {
  text-decoration: underline;
  font-size: 16px;
  color: grey;
  cursor: pointer;
  margin-bottom: 16px;
}

summary, summary:active {
  border: none;
}

details span {
  margin-top: 8px;
  display: block;
}

#header .btn-group {
  display: none;
}

.main-container {
  max-width: 1400px !important;
}
</style>

--- 

```{r setup, include=FALSE}
print(params)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
                      fig.path = params$output_figure, dev = "svg")
```


```{r data-needed, include=FALSE, eval=TRUE}
library(dplyr)
library(stringr)
library(MassExpression)
library(plotly)
library(kableExtra)

CompleteIntensityExperiment <- params$listInt$CompleteIntensityExperiment
IntensityExperiment <- params$listInt$IntensityExperiment
design <- colData(IntensityExperiment)

comparisonExperiments <- 
    listComparisonExperiments(CompleteIntensityExperiment)
```


<details>
  <summary>Relative Log Expression distributions</summary>
  <span>
    <p>It is useful to inspect the distribution of the Relative Log Expression (RLE) values to identify samples with largely unusual distributions. The RLE values for a protein are obtained by centering intensities to the protein medians, where the median is computed using only available intensities, i.e. non zero values. The RLE is computed on the log-transformed data before and after applying normalisation, when required. </p>
   <p>For a healthy experiment we expect:</p>
    <ul>
      <li>The RLE boxplots to have a similar median - centered around zero - across all samples </li>
      <li>The RLE boxplots to have a similar width of the boxes across samples </li>
    </ul>
     <p>If some samples show large deviations from the expected behaviour, it can be symptomatic of problems in the pre-processing of those samples.<p>
  </span>
</details> 

```{r rle-plots}
p_raw <- plot_rle_boxplot(IntensityExperiment, 
                    includeImputed = FALSE, plotRawRLE = TRUE)
p_raw
```
  