---
output:
  html_document:
    toc: no
    fig_caption: yes
    lib_dir: qc_report_files
params:
  listInt: empty
  output_figure: figures
---


<style type="text/css">
  .container-fluid, .main-container {
    max-width: inherit !important;
    padding: 0 !important;
  }
</style>

<script>
const handleLoaded = function () {
  const wrapperEl = document.querySelector('.js-plotly-plot');

  if (!wrapperEl) {
    return;
  }

  wrapperEl.style.width = '100%';
  wrapperEl.style.height = '100%';
  wrapperEl.style.marginBottom = '0';

  window.dispatchEvent(new Event('resize'));
};

document.addEventListener('DOMContentLoaded', handleLoaded, false);
</script>


```{r setup, include=FALSE}
print(params)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
                      fig.path = params$output_figure, dev = "svg")
```


```{r data-needed, include=FALSE, eval=TRUE}
library(dplyr)
library(stringr)
library(MassExpression)
library(plotly)

CompleteIntensityExperiment <- params$listInt$CompleteIntensityExperiment
IntensityExperiment <- params$listInt$IntensityExperiment
design <- colData(IntensityExperiment)

comparisonExperiments <- 
    listComparisonExperiments(CompleteIntensityExperiment)
```

  
```{r}
normalised <- FALSE
if(metadata(CompleteIntensityExperiment)$NormalisationAppliedToAssay != "None"){
  normalised <- TRUE
}

if(normalised){
  # Plot RLE of log2 raw intensity as well as RLE of normalised 
  plot_rle_boxplot(IntensityExperiment, CompleteIntensityExperiment, 
                      includeImputed = FALSE, 
                      plotRawRLE = FALSE,
                      title = "RLE of normalised log2(intensties)",
                      format = "html")
  
} else {
  text <- "No normalisation was applied to the data, therefore no difference is expected with the original log2(intensities) distribution."
}
```
  
  
`r if(!normalised) text`  
  